Psychological Needs During Intergroup Contact

### 2021-11-22 manuscript.tex
Real-Life Process Data

\section{Intergroup Contact Mechanisms}
\faQuestionCircle\ Not sure whether we need this section.

\faExclamationCircle\ This section has become way too complex (i.e., too many arguments to get to our own proposed work). I think we ultimately need to introduce the concept of interaction quality and that we don't necessarily know why interactions are perceived as positive, therefore we propose that we can look towards the motivational literature for this. The issue for me came up when I tried to give credit to past theoretical work (which I thought we need to acknowledge in some way).

@@

Interestingly, one concept that has arguably remained at the center of theoretical debates throughout the decades has been the role of 'positive' contact. \st{Although Gordon Allport was not generally optimistic of intergroup contact (especially if it was casual or by too deeply prejudiced individuals), he did see immense potential if only such interactions led to positive associations.} In his now famous chapter on 'the effects of contact', Gordon Allport (\citeyear{Allport1954b}) set out to summarize under what circumstances an interaction between groups tends to be positive, leading to favourable attitudes and reduced prejudice. In the years that followed, several additional conditions were proposed under which a positive intergroup contact would occur \citep[for a critical review see][]{Pettigrew1986}. As a counter-movement to this rather restrictive approach, with the beginning of the 21\textsuperscript{st} century attention had shifted towards investigating the psychological mechanisms of intergroup contact \citep[e.g. see,][]{Paolini2021}. With this shift in focus, the idea of 'positive contact' has seemingly seen a renaissance, where the adjective 'positive' is now not merely an evaluation of the outcome, but rather a feature of the interaction itself. As such, recent work has focused on the role of 'perceived interaction quality' \citep[e.g.,][]{Brown2007, Voci2003} or 'interaction valence' \citep[e.g.,][]{Tropp2016, Barlow2012}, to show that only if an interaction is perceived as positive will it lead to more favourable intergroup relations. And inversely interactions that are perceived as negative have the strong propensity to harm outgroup attitudes. However, relatively little research has investigated why interactions are perceived as positive.

@@

\section{Process Data}
\begin{itemize}
    \item retrospective vs. near-time data
    \item need for longitudinal \citep[][]{Pettigrew1998, Pettigrew2008, Pettigrew2008b, Pettigrew2011} and real-life data \citep[][]{MacInnis2015, McKeown2017}
    \item barriers
    \item innovations like 'contact logger' \citep[][]{Keil2020}, and FormR \citep[][]{Arslan2020} make this possible now \citep[also see, e.g.,][]{ODonnell2021}
\end{itemize}

\faQuestionCircle\ Not sure where this goes: To ensure that our sample would have a considerable number of intergroup contacts we focused on the minority group perspective in our second study. We followed a group of young migrants who had (daily) intergroup contacts with majority Dutch people. This design allowed us to test whether intergroup interactions and the fulfillment of psychological needs could jointly predict the development of attitudes towards the outgroup (i.e., the Dutch host society).

>>>>

\section{Intergroup Contact Mechanisms}
\faQuestionCircle\ \textit{Not sure whether we need this section.}

\faExclamationCircle\ \textit{This section has become way too complex (i.e., too many arguments to get to our own proposed work). I think we ultimately need to introduce the concept of interaction quality and that we don't necessarily know why interactions are perceived as positive, therefore we propose that we can look towards the motivational literature for this. The difficulties started for me when I tried to give credit to past theoretical work (which I thought we need to acknowledge in some way).}

@@

Interestingly, one concept that has arguably remained at the center of theoretical debates throughout the decades has been the role of 'positive' contact. In his now famous chapter on 'the effects of contact', Gordon Allport (\citeyear{Allport1954b}) set out to summarize under what circumstances an interaction between groups tends to be positive, leading to favourable attitudes and reduced prejudice. In the years that followed, several additional conditions were proposed under which a positive intergroup contact would occur \citep[for a critical review see][]{Pettigrew1986}. As a counter-movement to this rather restrictive approach, with the beginning of the 21\textsuperscript{st} century attention had shifted towards investigating the psychological mechanisms of intergroup contact \citep[e.g. see,][]{Paolini2021}. With this shift in focus, the idea of 'positive contact' has seemingly seen a renaissance, where the adjective 'positive' is now not merely an evaluation of the outcome, but rather a feature of the interaction itself. As such, recent work has focused on the role of 'perceived interaction quality' \citep[e.g.,][]{Brown2007, Voci2003} or 'interaction valence' \citep[e.g.,][]{Tropp2016, Barlow2012}, to show that only if an interaction is perceived as positive will it lead to more favourable intergroup relations. And inversely interactions that are perceived as negative have the strong propensity to harm outgroup attitudes. However, relatively little research has investigated why interactions are perceived as positive.

@@

\section{Real-Life Process Data}
Over the past two decades several reviewers of the field have advocated that to truly understand intergroup contacts, there is a need for studies that collect longitudinal \citep[][]{Pettigrew1998, Pettigrew2008, Pettigrew2008b, Pettigrew2011} and real-life data outside the lab \citep[][]{MacInnis2015, McKeown2017}. The reasoning behind these calls for longitudinal real-life data has been manifold. Among the most pressing issues is concern that past investigations of intergroup contact have either focused on the dynamics of individual interactions but within artificial laboratory settings or have collected data situated within the lived experiences but used retrospective self-report data that asked about past interactions in general. The collection of data over time would, thus, allow researchers to follow the development of intergroup relations as they develop across multiple interactions. At the same time, such longitudinal data would also be situated within the real-life experiences of the participant. Additionally, such experience-sampling data can be close to the intergroup interactions would largely mitigate recall biases. Moreover, intensive longitudinal data often allows to capture large amounts of high-quality data with relatively few participants.

In the past such data collections were often unfeasible because they were either physically impractical or too expensive. However, recent technological developments allow us to easily collect experience sampling data on mobile devices \citep[e.g.,][]{Keil2020} or using web-based applications \citep[e.g.,][]{Arslan2020}. At the same time, analytical methods for such more complex data have become more readily available, making the analyses more approachable \citep[see, e.g.,][]{ODonnell2021}. Given these, technological and methodological developments, we were able to collect a large amount of real-life data following the daily intergroup interactions of recent migrants with the majority group members.
